Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex

There has been plenty of previous work that aims at \emph{verifying} a given
controller designed by the engineer.  Recent work can show the of stability
digital controllers with considerations to implementation aspects, i.e.,
fixed-point arithmetic and the word length used~\cite{Bessa16}.  This work
exploits advances in bit-accurate verification of C programs to obtain a
verifier for software-implemented digital control.

@@

\item We exploit a CEGIS-based approach that uses inductive synthesis
together with a bit-precise formal verification algorithm for synthesising
correct-by-design robust digital controllers for non-fragile closed-loop
stability.

\item Experimental results with our synthesiser show that the
combination of interval arithmetic to represent the controller coefficients
and a two-stage verification approach to continuously refine precision
enables us to compute a parametric, sound solution for $14$ out of $15$
digital stabilizing controllers for a set of continuous and discrete plants
with parametric uncertainties.

@@

The digital controllers synthesised using the algorithm we present in this
paper are typically used in closed loops with continuous (and physical)
plants.  Thus, the proposed approach has to consider dynamics of continuous
parts of the system (i.e., the plant) and the discrete parts (i.e., the
digital controller).  To obtain a joint model, the discretise the continuous
plant.  We only consider transfer function models, and require a $z$-domain
transfer function that captures all aspects of the continuous plant (with a
Laplace domain transfer function $G(s)$) and the sampling and hold process.

Note that $G(z)$ is a discrete model of a real-domain (and continuous)
plant, i.e., the continuous model of the plant must be discretised to obtain
the discrete equivalent coefficients via ZOH discretisation.

@@

Although there are several discretisation methods available in the
literature~\cite{Franklin15}, the zero-order hold (ZOH) discretisation is
more suitable for representing the sample and hold processes that are
typically employed in complex systems~\cite{istepanian2012digital}, i.e.,
the ZOH discretisation models the exact effect of sampling and DAC
interpolation over the plant.

\begin{myassumption}
%
The Sample and Hold of the ADC and the ZOH of the DAC are synchronized,
i.e., there is no delay between sampling the plant output at ADC and
updating the DAC accordingly.  The DAC interpolator is an ideal ZOH.
%
\end{myassumption}

@@

Lemma~\ref{eq:pulsetf} ensures the poles and zeros matching with
$\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
operations and includes the ZOH dynamics in the $(1-z^{-1})$ term, that is
sufficient for the stability studies over $G(s)$.

>>>>

There has been plenty of previous work that aims at \emph{verifying} a given
controller designed by the engineer.  Recent work can show the stability
digital controllers with considerations to implementation aspects, i.e.,
fixed-point arithmetic and the word length used~\cite{Bessa16}.  This work
exploits advances in bit-accurate verification of C programs to obtain a
verifier for software-implemented digital control.

@@

\item We designed and implemented an automatic approach for 
generating {\em corect-by-construction} digital controllers that is 
based on state-of-the-art inductive synthesis techniques.
Our application of program synthesis is not trivial 
and requires addressing challenges specific to
control systems such as the effects of quantisers 
and FWL. In particular, we found that a two-stage 
verification engine that continuously refines the precision
of the fixed-point representation is key to the performance of our approach.

\item We provide experimental results showing that
our fully automatic program synthesis based approach is able to synthesise 
stable controllers
%sound parametric solutions for digital stabilizing controllers
for a set of intricate benchmarks taken from 
the literature in a reasonable amount of time 
(the median runtime for our benchmark set is 197s, 
implying that half of the controllers can be synthesised in less
than 5 minutes).

%% \item We exploit a CEGIS-based approach, that uses inductive synthesis
%% in conjunction with a formal verification algorithm, for synthesising 
%% correct-by-design robust digital controllers for non-fragile closed-loop 
%% stability.

%% \item Experiments obtained with our synthesiser show that the combination 
%% of interval arithmetic to represent the controller coefficients and a two-stage 
%% verification approach to continuously refine precision, we are able to compute 
%% a parametric sound solution for $14$ out of $15$ digital stabilizing controllers 
%% given a set of continuous and discrete plant with parametric uncertainties.

@@

The digital controllers synthesised in this paper are typically used in
closed loops with continuous (and physical) plants.  Thus, the proposed
approach has to consider dynamics of continuous parts of system ({\it e.g.},
plant) and discrete parts ({\it e.g.}, digital controller).

For this purpose, the design procedure is based on a discretised model for a
continuous plant.  Considering only transfer function models, we are
interested in a $z$-domain transfer function that considers all the aspects
about the continuous plant ($G(s)$) and the sampling and hold process.

Note that $G(z)$ is a discrete model of a real (and continuous) plant, i.e.,
a continuous model of the plant must be discretised to obtain the discrete
equivalent coefficients via ZOH discretisation.

@@

Although there are several discretisation methods available in the
literature~\cite{Franklin15}, the zero-order hold (ZOH) discretisation is
more suitable for representing the sample and hold processes that are
typically employed in complex systems~\cite{istepanian2012digital}, {\it
i.e.}, the ZOH discretisation models the exact effect of sampling and DAC
interpolation over the plant.

\begin{myassumption}
%
The Sample and Hold of the ADC and the ZOH of the DAC are synchronized, {\it
i.e.}, there is no delay between sampling the plant output at ADC and
updating the DAC accordingly.  The DAC interpolator is an ideal ZOH.
%
\end{myassumption}

@@

The lemma \ref{eq:pulsetf} is ensures the poles and zeros matching with $\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$ operations and includes the ZOH dynamics in the $(1-z^{-1})$ term, that is sufficient for the stability studies over $G(s)$
